\tiny \begin{longtable} {|l|p{0.1\textwidth}|p{0.1\textwidth}|p{0.35\textwidth}|l|l|l|p{0.11\textwidth}|} \caption{Team members for Data Production for Rubin Observatory  FY21 \label{tab:teamsNames}}\\
\hline
\textbf{WBS}&\textbf{Team}&\textbf{Role Title}&\textbf{Role Description}&\textbf{Institution}&\textbf{FY21 FTE}&\textbf{FY22 FTE}&\textbf{Staff} \\ \hline
{3.1a}&{Data Production Management}&{Associate Director for Data Production}&{The AD of the Data Production Department is one of the principal leaders of the Rubin Observatory operations phase. This position requires a Ph.D. level astronomer with extensive astronomical survey and science management experience, and reports directly to the Rubin Observatory Director. The primary responsibilities of this position include the management of the Data Production Department, participation in the leadership of Rubin Observatory survey, and coordination with other Rubin Observatory Departments. The AD for Data Production also has overall responsibility and authority for safely running the Rubin Observatory Data Facilities (DF) including the generation of prompt data products (alerts) and the annual data release processing. This person will supervise a technical staff that will be responsible for all aspects of data processing, preparation of data products, archiving, and operation of the Chilean, French and UK DACs/ DFs, as well as the US DF. They will be responsible for coordinating with project level Contract Management and Supplier Management when dealing with issues of business impact, and accountable for ensuring a disaster recovery plan is effective and able to be invoked. The AD of Data Production is also responsible for supervising the data flow from the Recinto to the USDF.}&{AURA}&{0.50}&{0.50}&{O'Mullane, William} \\ \hline
{3.1c}&{Data Production Management}&{Data Production Advisor - US DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Production in terms of execution across the data facilities.  }&{SLAC}&{0.25}&{0.25}&{Dubois, Richard} \\ \hline
{3.1c.1}&{Data Production Management}&{Data Production Advisor - Fr DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Production in terms of execution across the data facilities.  }&{IN2P3}&{0.25}&{0.25}&{Hernandez, Fabio} \\ \hline
{3.1c.2}&{Data Production Management}&{Data Production Advisor - UK DF}&{Each Rubin Observatory Data Facility (US, French and UK) has an advisory role to the AD for Data Production in terms of execution across the data facilities.  }&{UK}&{0.25}&{0.25}&{Beckett, George} \\ \hline
{3.2a}&{Infrastructure and Support}&{US Data Facility Lead}&{Provides management and oversight for the US Data Facility. Provides for evolution of service architecture and supporting ITC. Responsible for design and evolution of the US DF and its interactions with the French and UK Data Facilities, and the Chilean and other DACs.}&{SLAC}&{0.25}&{0.50}&{Dubois, Richard} \\ \hline
{3.2b}&{Infrastructure and Support}&{US DF Technical Lead - SLAC}&{Responsible for leading the Data, Compute and IT Security team involved in providing foundational services for file-based data, data resident in database engines, and facility-wide services including AAA and operational network security infrastructure.}&{SLAC}&{0.25}&{0.25}&{Mueller, Fritz} \\ \hline
{3.2b.1}&{Infrastructure and Support}&{US DF Technical Lead - NOIRLab}&{Responsible for leading the Data, Compute and IT Security team involved in providing foundational services for file-based data, data resident in database engines, and facility-wide services including AAA and operational network security infrastructure.}&{NCSA}&{0.25}&{0.25}&{Butler, Michelle} \\ \hline
{3.2c}&{Infrastructure and Support}&{DF/ IDACs Technical Coordinator}&{Coordinate technical needs among the collection of Data Facilities and IDACS. Respond to issues that come up day to day in connections, transfers etc.}&{US DF}&{0.00}&{0.25}& \\ \hline
{3.2d}&{Infrastructure and Support}&{Data Movement Engineer}&{Maintain Rucio system which will be involved in the tracking and moving of data between multiple sites,including hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites. This is in close conjunction with the Storage Engineers in the Data Facilities. Rucio is an open source HEP product which we have adopted on Rubin Observatory.}&{NCSA}&{0.25}&{0.25}&{Kowalik, Nic} \\ \hline
{3.2d}&{Infrastructure and Support}&{Data Movement Engineer}&{Maintain Rucio system which will be involved in the tracking and moving of data between multiple sites,including hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites. This is in close conjunction with the Storage Engineers in the Data Facilities. Rucio is an open source HEP product which we have adopted on Rubin Observatory.}&{Fermilab}&{0.50}&{0.75}&{White, Brandon} \\ \hline
{3.2d}&{Infrastructure and Support}&{Data Movement Engineer}&{Maintain Rucio system which will be involved in the tracking and moving of data between multiple sites,including hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites. This is in close conjunction with the Storage Engineers in the Data Facilities. Rucio is an open source HEP product which we have adopted on Rubin Observatory.}&{SLAC}&{0.25}&{0.50}&{Hanushevsky, Andy} \\ \hline
{3.2e}&{Infrastructure and Support}&{Workflow/ Load Management Engineer}&{Maintain smooth operation of workflow/ workload tools for pipeline operation.}&{BNL}&{0.00}&{0.25}& \\ \hline
{3.2g}&{Infrastructure and Support}&{Database Engineer (Qserv) - SLAC}&{Develops, maintains, and implements the science Databases e.g. QSERV database, data butler, Prompt Products Database. May also work on other middleware as needed.}&{SLAC}&{0.50}&{0.25}&{Mueller, Fritz} \\ \hline
{3.2g}&{Infrastructure and Support}&{Database Engineer (Qserv) - SLAC}&{Develops, maintains, and implements the science Databases e.g. QSERV database, data butler, Prompt Products Database. May also work on other middleware as needed.}&{SLAC}&{0.75}&{1.00}&{Gaponenko, Igor} \\ \hline
{3.2g}&{Infrastructure and Support}&{Database Engineer (Qserv) - SLAC}&{Develops, maintains, and implements the science Databases e.g. QSERV database, data butler, Prompt Products Database. May also work on other middleware as needed.}&{SLAC}&{0.50}&{0.50}&{Pease, Nate} \\ \hline
{3.2g}&{Infrastructure and Support}&{Database Engineer (Qserv) - SLAC}&{Develops, maintains, and implements the science Databases e.g. QSERV database, data butler, Prompt Products Database. May also work on other middleware as needed.}&{SLAC}&{0.50}&{0.50}&{Gates, John} \\ \hline
{3.2g.1}&{Infrastructure and Support}&{Dev/ Ops Software Engineer - IN2P3}&{Develops, maintains, and implements DF software, including: QSERV database, data butler, DAX, Alert Filtering Service, orchestration software, workflow software, data backbone software, integration testing framework, authentication services, pipeline construction tools, operational fabric codes, logging, messaging, monitoring and health and status software, hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites.}&{IN2P3}&{0.13}&{0.19}&{Fabrice James} \\ \hline
{3.2g.1}&{Infrastructure and Support}&{Dev/ Ops Software Engineer - IN2P3}&{Develops, maintains, and implements DF software, including: QSERV database, data butler, DAX, Alert Filtering Service, orchestration software, workflow software, data backbone software, integration testing framework, authentication services, pipeline construction tools, operational fabric codes, logging, messaging, monitoring and health and status software, hosting environment for Rubin Observatory Data Space, Data Space batching services, and bulk export to other sites.}&{IN2P3}&{0.13}&{0.19}&{Elles, Sabine} \\ \hline
{3.2j}&{Infrastructure and Support}&{Wide Area Network Technical Manager}&{Responsible for providing coordination amongst and managing relationships with the four independent WAN operators. Acts as the interface for services provided to the US DF in the context of the WAN. Responsible for managing the risk associated with each WAN operator, including developing mitigation strategies and proposed project responses to credible risks. Leads the Joint Wide Area Network Working Group. Well connected to DOE ESNet.}&{Fermilab}&{0.38}&{0.38}&{Demar, Phil} \\ \hline
{3.2k}&{Infrastructure and Support}&{Wide Area Network Architect}&{Familiar with WAN implementation technologies generally available in the networks supporting the Rubin Observatory. Familiar with technology roadmap of the ESNet WAN provider. Synthesizes and evolves network techniques and provisioning supporting the Rubin Observatory mission, as network technology evolves. Drawn from staff of WAN groups but explicitly supported by and work in the context of the Rubin Observatory.}&{Fermilab}&{0.38}&{0.75}&{Bobyshev, Andrey} \\ \hline
{3.2l}&{Infrastructure and Support}&{Generalist Software Engineer}&{General and broad computing skills, responding to the myriad of issues/ needs that will come up - including via user support tickets.}&{SLAC}&{0.25}&{0.50}&{Van Klaveren, Brian} \\ \hline
{3.2m}&{Infrastructure and Support}&{Cluster Manager}&{Provides workload management (eg kubernetes) of the clusters.}&{SLAC}&{0.25}&{0.25}&{SLAC TID Rubin Group Leader \#1} \\ \hline
{3.2n}&{Infrastructure and Support}&{Code Librarian}&{Maintain and improve the builds for the various data production software products. This includes fixing the continuous integration builds and improving the packaging system (currently aiming for Conda but could potentially move to another system over ten years). With hundreds of packages this is not a trivial task. This role would also support the observatory software builds which could potentially remain different to the Data Production builds.}&{SLAC}&{0.00}&{0.25}&{SLAC TID Rubin Group Leader \#1} \\ \hline
{3.2o}&{Infrastructure and Support}&{AVS Engineer}&{The Alert Verification System Engineer will implement the algorithms for the AVS and agree with the Alert Production Pipeline Group how to best integrate them in the system. This interface has not yet been agreed but will certainly need updating and work during the early years of operations. This includes monitoring the system and ensuring it meets the US federal agencies needs.}&{LLNL}&{0.50}&{1.00}&{LLNL AVS Engineer \#1} \\ \hline
{3.2o}&{Infrastructure and Support}&{AVS Engineer}&{The Alert Verification System Engineer will implement the algorithms for the AVS and agree with the Alert Production Pipeline Group how to best integrate them in the system. This interface has not yet been agreed but will certainly need updating and work during the early years of operations. This includes monitoring the system and ensuring it meets the US federal agencies needs.}&{LLNL}&{0.50}&{1.00}&{LLNL AVS Engineer \#2} \\ \hline
{3.2w}&{Infrastructure and Support}&{Catalog Manager - UK}&{The catalog manager ensures the day-to-day operations of the astronomical catalog database at IN2P3. This includes ingesting new data and removing and archiving obsolete catalogs. They also interact with the data wrangler to ensure that the catalog data produced at other sites are imported and ingested into the IN2P3 catalog and that the catalog data produced at IN2P3 is ingested into the local catalog and replicated to other sites. They also ensure that the software releases for the catalog database are compatible with those releases used at other sites operating a catalog database, in particular, the USDF.}&{UK}&{0.00}&{0.50}& \\ \hline
{3.3a}&{Data and Processing Architecture}&{DPA Lead}&{Organizes the software maintenance effort and assigns work in a way that provides for continuity of maintenance for all Rubin Observatory maintained software. Is primarily responsible for further defining and enforcing software engineering rules related to maintenance, including maintenance of documentation, correct security practices, testing, and other aspects of delivery of a complete change set. Ensures that software tasks are consistent with authorized changes. Carries share of maintenance load. Participates in reviews.}&{AURA}&{0.25}&{0.38}&{Jenness, Tim} \\ \hline
{3.3b}&{Data and Processing Architecture}&{Data Engineer}&{Hold project history on data models etc and guide VO developments}&{IPAC}&{0.00}&{0.10}&{Dubois-Felsmann, Gregory} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.25}&{0.50}&{Salnikov, Andy} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.25}&{0.50}&{Pease, Nate} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.50}&{0.50}&{Wittgen, Matthias} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.25}&{0.25}&{Lim, K-T} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{BNL}&{0.40}&{0.50}&{Ye, Shuwei} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{BNL}&{0.60}&{0.50}&{Padolski, Sergey} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.75}&{1.00}&{Campaign Tooling Engineer \#1} \\ \hline
{3.3c}&{Data and Processing Architecture}&{Service Software Engineer - SLAC}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{SLAC}&{0.25}&{0.25}&{Campaign Tooling Engineer \#2} \\ \hline
{3.3f}&{Data and Processing Architecture}&{Service Software Engineer - NOIRLab}&{Develops, maintains, and implements pipeline and workflow software, including: Data Butler, orchestration software, workflow/ workload software, integration testing framework, pipeline construction tools, and pipeline infrastructure libraries.}&{NCSA}&{0.30}&{0.30}&{Gower, Michelle} \\ \hline
{3.4a}&{Execution}&{Lead Production Scientist}&{Responsible for leading the Execution Team. This includes responsibility for managing the activities of the team members, planning work, and reporting on progress and issues to the next level of management. Additionally, the Lead Production Scientist must possess all of the skills and qualifications of a Production Scientist.}&{SLAC}&{0.25}&{0.50}&{Chiang, Hsin-Fang} \\ \hline
{3.4d}&{Execution}&{Data Release Production Scientist}&{Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.}&{Fermilab}&{0.25}&{0.50}&{Yanny, Brian} \\ \hline
{3.4d.1}&{Execution}&{Data Release Production Scientist - IN2P3}&{Responsible for processing and database ingestion of Batch (DRP) Data Products. This includes responsibility for: acting as the Scientific Code Liaison, hardware and software deployment, oversight and responsibility for processing execution, prompt SDQA and response, alert filtering service operations, and external (community) broker operations.}&{IN2P3}&{0.25}&{0.50}&{Boutigny, Dominique} \\ \hline
{3.4e}&{Execution}&{Data Release Processing Scientist - SLAC}&{Perform day to day operation of the DRP pipeline. Expert in the technical operation of the DRP pipeline. Address bottlenecks, failure modes. }&{Fermilab}&{0.25}&{0.50}&{Kuropatkin, Nikolay} \\ \hline
{3.4e.1}&{Execution}&{Data Release Processing Scientist - NOIRLab}&{Perform day to day operation of the DRP pipeline. Expert in the technical operation of the DRP pipeline. Address bottlenecks, failure modes. }&{NCSA}&{0.25}&{0.25}&{Adamow, Monika} \\ \hline
{3.4e.2}&{Execution}&{Data Release Processing Scientist - IN2P3}&{Perform day to day operation of the DRP pipeline. Expert in the technical operation of the DRP pipeline. Address bottlenecks, failure modes. }&{IN2P3}&{0.25}&{0.75}& \\ \hline
{3.5a}&{Algorithms and Pipelines}&{Lead of Algorithms and Pipelines}&{Responsible for the leadership and coordination of the Algorithms and Pipelines Team, the scientific integrity of Alert Production and Data Releases, and interaction and coordination with the Lead Community Scientist, Lead Scheduler Scientist, and the Lead Production Scientist. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience, or a software engineer with extensive astronomical experience.}&{Princeton}&{0.25}&{0.38}&{AlSayyad, Yusra} \\ \hline
{3.5b}&{Algorithms and Pipelines}&{Alert Production Pipeline Group Leader}&{Applying extensive astronomical knowledge, including solar system, explosive transients, and time-domain surveys in general, and Rubin Observatory software experience, this role acts as product owner for the prompt processing pipelines and oversees the day-to-day work of the Alert Production Pipeline Scientists. Recommends changes to Alert Production Pipelines and supports or rejects software changes based on scientific validation of new algorithms and an understanding of their impact on required computational resources. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise.}&{UW}&{0.25}&{0.38}&{Bellm, Eric} \\ \hline
{3.5c}&{Algorithms and Pipelines}&{Lead Alert Production Algorithms Scientist}&{This role provides leadership for the algorithmic development of the prompt processing pipelines, such as image differencing and template generation. This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise.}&{UW}&{0.00}&{0.50}&{Sullivan, Ian} \\ \hline
{3.5d}&{Algorithms and Pipelines}&{Alert Production Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.}&{UW}&{0.25}&{0.38}&{Sedaghat, Nima} \\ \hline
{3.5d}&{Algorithms and Pipelines}&{Alert Production Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.}&{UW}&{0.25}&{0.38}&{Morrison, Chris} \\ \hline
{3.5d}&{Algorithms and Pipelines}&{Alert Production Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.}&{UW}&{0.00}&{0.25}&{Heinze, Ari} \\ \hline
{3.5d}&{Algorithms and Pipelines}&{Alert Production Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.}&{UW}&{0.25}&{0.38}&{Parejko, John} \\ \hline
{3.5e}&{Algorithms and Pipelines}&{Alert Production Pipeline Scientist - SLAC}&{This role combines an understanding of one or more specific prompt processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Prompt Processing Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive time-domain survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Alert Production Pipeline Group Leader.}&{Fermilab}&{0.50}&{0.50}&{Herner, Ken} \\ \hline
{3.5g}&{Algorithms and Pipelines}&{Data Release Pipeline Group Leader}&{Applying extensive astronomical knowledge of all key Rubin Observatory science cases  (including dark energy, galaxies, and stars), wide-field astronomical surveys, and Rubin Observatory software, this role acts as product owner for the data release processing pipelines and oversees the day-to-day work of the Data Release Pipeline Scientists. Recommends changes to Data Release Production Pipelines and supports or rejects software changes based on scientific validation of new algorithms and an understanding of their impact on required computational resources. Defines, develops, and maintains the Rubin Observatory scientific processing pipelines' overall architecture, advising Pipeline Scientists to ensure that the overall Rubin Observatory Science Pipelines form a coherent whole, interfacing with the Middleware Team.  This position requires a Ph.D. level astronomer with extensive astronomical survey and software experience or a software engineer with extensive astronomical expertise. Expert in software architecture with expertise in scientific software design and the Rubin Observatory software system preferred.  Reports to the Lead of Algorithms and Pipelines. }&{Princeton}&{0.50}&{0.50}&{Bosch, Jim} \\ \hline
{3.5h}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{Princeton}&{0.25}&{0.38}&{Saunders, Clare} \\ \hline
{3.5h}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{Princeton}&{0.25}&{0.25}&{Moolekamp, Fred} \\ \hline
{3.5h}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{Princeton}&{0.25}&{0.25}&{Taranu, Dan} \\ \hline
{3.5h}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{Princeton}&{0.25}&{0.38}&{Kannawadi, Arun} \\ \hline
{3.5h}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - NOIRLab}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{Princeton}&{0.25}&{0.38}&{Lust, Nate} \\ \hline
{3.5i}&{Algorithms and Pipelines}&{Data Release Pipeline Scientist - SLAC}&{This role combines an understanding of one or more specific data release processing processing science use cases with software engineering expertise and an understanding of the Rubin Observatory Science Pipelines to work in conjunction with the Science Software Engineering Group to modify, extend, and update the Data Release Pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and software development experience, or a software engineer with extensive astronomical experience. Reports to the Data Release Pipeline Group Leader.}&{LLNL}&{0.50}&{0.50}&{Meyers, Josh} \\ \hline
{3.5k}&{Algorithms and Pipelines}&{Lead Calibration Scientist}&{Together with the Calibration Support Scientist at the summit, ensures that data is available to enable proper astrometric and photometric calibration of Rubin Observatory data as part of regular pipeline processing. The Lead Calibration Scientist reports to the Lead of the Algorithms and Pipelines Team. The Lead Calibration Scientist position requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience: it is desirable for this position to be filled by a person who contributed to the construction of the Calibration Products Production pipeline.}&{D4D Ltd}&{0.25}&{0.38}&{Fisher-Levine, Merlin} \\ \hline
{3.5l}&{Algorithms and Pipelines}&{Calibration Group Leader}&{Ensures that data is available to enable proper astrometric and photometric calibration of Rubin Observatory data as part of regular pipeline processing. This role combines an understanding of one or more specific data release processing science use cases with software engineering expertise to modify, extend, and update the first steps of both the prompt processing and data release pipelines in response to emergent scientific needs, community requests, and bug reports. This role requires a Ph.D. level astronomer with extensive astronomical survey and Rubin Observatory software experience. Prefer someone who contributed to the construction of the Calibration Products Production Pipeline}&{Princeton}&{0.00}&{0.25}&{Waters, Chris} \\ \hline
{3.5n}&{Algorithms and Pipelines}&{Calibration Consultant}&{Advises and reports to the Calibration Group Leader. The Consultant position is a senior position filled by fractions of individuals with deep and intimate knowledge of the Rubin Observatory Data Management system, presumably from the construction period.}&{Princeton}&{0.25}&{0.38}&{Lupton, Robert} \\ \hline
{3.5o}&{Algorithms and Pipelines}&{AVS Oversight Liaison}&{A member of the Alerts team should work closely with the AVS Engineers to enure proper integration of the algoritms and correct application of any data screening. }&{UW}&{0.00}&{0.25}& \\ \hline
{3.6a}&{Service Quality and Reliability Engineering}&{Technical Lead/ Manager}&{Responsible for technical leadership and management of the Service Quality and Reliability Engineering Team. This includes running stand ups and looking after budgets and staff issues as well as making technical calls where decisions are needed. The technical lead is responsible overall for the architecture of the team’s services and for ensuring it is fit for purpose for the observatory’s evolving needs. They also represent the team’s work both inside the organization and to the astronomical and computing technical community.}&{AURA}&{0.50}&{0.50}&{Economou, Frossie} \\ \hline
{3.6b}&{Service Quality and Reliability Engineering}&{DevOps Infrastructure Engineer - NOIRLab}&{Generalist software engineers who work through the entire software stack. A DevOps engineer must be able to understand the software and infrastructure enough to know it is working well. They must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service. }&{AURA}&{0.00}&{0.25}& \\ \hline
{3.6b.1}&{Service Quality and Reliability Engineering}&{Senior Full Stack and Documentation Engineer - NOIRLab}&{A Senior Full-Stack Engineer is a DevOps Engineer who is versed in architecture and implementation of both backend and frontend architectures. They are able to synthesize requirements, propose system architectures and independently implement services. They have advanced skills in DevOps engineering, including Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
A Documentation Engineer is well versed in architecting effective ways to support documentation oriented workflows such as documentation continuous delivery systems and integration with communication platforms. They have advanced skills in service implementation and deployment, familiarity with documentation infrastructure libraries such as Sphinx, and best practices in software documentation, including code-level, package-level and user guides.
}&{AURA}&{0.25}&{0.38}&{Sick, Jonathan} \\ \hline
{3.6b.2}&{Service Quality and Reliability Engineering}&{Security Architect /  Senior DevOps Engineer  - NOIRLab}&{A Security Architect is a software engineer with advanced expertise in designing and building software services with particular regard to security concerns such as authentication \& authorisation, hardening, auditability, penetration testing and dependency management.  A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
}&{AURA}&{0.25}&{0.38}&{Allbery, Russ} \\ \hline
{3.6c}&{Service Quality and Reliability Engineering}&{Front End engineer /  Senior Front End Engineer}&{Front-end engineers with strong javascript skills, web services architecture, user interface design and astronomical search and visualisation to focus on the Science Platform portal. At least one of these FTEs needs to be at IPAC at a senior engineer level to reflect our current technical investment in Firefly and coordinate effort appropriately in conjunction with other IPAC Firefly development. An appropriately skilled FTE may be found elsewhere or may be added to an IPAC subcontract if available}&{AURA}&{0.00}&{0.25}& \\ \hline
{3.6c}&{Service Quality and Reliability Engineering}&{Front End engineer /  Senior Front End Engineer}&{Front-end engineers with strong javascript skills, web services architecture, user interface design and astronomical search and visualisation to focus on the Science Platform portal. At least one of these FTEs needs to be at IPAC at a senior engineer level to reflect our current technical investment in Firefly and coordinate effort appropriately in conjunction with other IPAC Firefly development. An appropriately skilled FTE may be found elsewhere or may be added to an IPAC subcontract if available}&{AURA}&{0.00}&{0.25}& \\ \hline
{3.6d}&{Service Quality and Reliability Engineering}&{Science Platform \& Production Services Engineer}&{A Science Platform and Production Services Engineer is responsible for identifying and resolving  issues with production services, including user-facing services such as the Science Platform as well as facility services (such as deployments of the Science Platform at the telescope summit). They are also responsible for evolving services on the basis of rapidly changing user demand, for example the JupyterLab-based component of the Science Platform. They have strong software engineering skills including coding, testing and service deployment and can perform technical work in an independent manner.}&{AURA}&{0.25}&{0.38}&{Thornton, Adam} \\ \hline
{3.6d.1}&{Service Quality and Reliability Engineering}&{Services Architect /  Senior DevOps Engineer}&{A Services Architect is a software engineer with advanced expertise in designing and building software services with particular regard to scalability, performance, deployment infrastructure and interface design. They are able to synthesize requirements, propose system architectures and independently implement services.
A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
}&{AURA}&{0.25}&{0.38}&{Banek, Christine} \\ \hline
{3.6e}&{Service Quality and Reliability Engineering}&{Senior Scientific Programmer /  Data Exploration Specialist}&{A Senior Scientific Programmer has deep domain expertise and is adept in capturing and implementing data analysis solutions. Their scientific background allows them to anticipate user data exploration needs and other requirements and to effectively communicate them to other engineers on their team.
A Data Exploration Specialist communicates data exploration needs to the engineers, documents and develops tools, demonstrates how to achieve scientific goals with the tools provided. This would explicitly include technical consultations to the Community Engagement Team and EPO scientists. Their scientific background allows them to translate the technical needs of the users of services (external and internal) into an engineering request, as well as functioning as liaison to other interrelated systems (in particular Middleware and Infrastructure) to which Science Platform services have a dependence.
}&{AURA}&{0.25}&{0.38}&{Fausti, Angelo} \\ \hline
{3.6e.1}&{Service Quality and Reliability Engineering}&{Senior Devops Engineer /  Data Engineer}&{A Senior Devops Engineer has advanced skills in DevOps engineering, including Software Engineering, Continuous Deployment and Infrastructure As Code, and must also be able to improve the infrastructure and debug problems which can span hardware, network and operating system all the way to the end user delivered service.
A Data Engineer is a software engineer with the ability to model and abstract data flow and representation, as well as design and implement appropriate systems for the effective curation and visualisation of particular kinds of data (eg. time series).
A Data Exploration Specialist communicates data exploration needs to the engineers, documents and develops tools, demonstrates how to achieve scientific goals with the tools provided. This would explicitly include technical consultations to the Community Engagement Team and EPO scientists. Their scientific background allows them to translate the technical needs of the users of services (external and internal) into an engineering request, as well as functioning as liaison to other interrelated systems (in particular Middleware and Infrastructure) to which Science Platform services have a dependence.}&{AURA}&{0.25}&{0.38}&{Krughoff, Simon} \\ \hline
\end{longtable} \normalsize
